### 2016-06-29 sec3_definitions.tex
Several minor changes
Needs to proofread more

We take $T=(1,2,3,5,6)$ as an example, which can be decomposed into two segments $(1,2,3)$ and $(5,6)$. $T$ is not $3$-consecutive since the length of $(5,6)$ is $2$. Thus, it is safe to say either $T$ is $1$-consecutive or $2$-consecutive. On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$. It is worth noting that $T$ is not $1$-connected because the gap between $T[3]$ and $T[4]$ is 2 (i.e., 5-3=2).

Given a trajectory database discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textit{significance:} $|O| \geq M$; (3) \textit{duration:} $|T| \geq K$; (4) \textit{consecutiveness:} $T$ is L-consecutive; and (5) \textit{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$.  By customizing these parameters, our pattern can 
express other patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we achieve the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
\textbf{Pattern} & $M$ & $K$ & $L$ & $G$ & \textbf{Clustering} \\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & Disk-based\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & Disk-based \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & Density-based\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & Density-based \\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & Density-based\\ 
\hline 
\end{tabular} 
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value. $M$ represents the 
object \emph{size} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.}
\label{tbl:patterns}
\end{table}
\eat{ 
It is also observable that the number of patterns in GCMP could be exponential under some parameter settings (i.e., 
when expressing \emph{swarm}). In particular, given a parameter $M$, if a pattern $P$ is valid, then any subset of $P$ with 
size $M$ is also a valid pattern. This results in additional $\Sigma_{M\geq i \geq |P.O|} {|P.O| \choose i}$ patterns,
which is clearly overwhelming and redundant. For all these patterns, output $P$ is sufficient. Therefore, we define the \emph{Closed General Co-Movement Pattern} as follows:

@@

Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
We currently expose both disc-region based clustering and DBSCAN as options to the users. In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMP from large-scale trajectory datasets. Before we move on to the algorithmic part, we list the notations that are used in the following sections.

\begin{table}[h]\scriptsize
\centering
\begin{tabular}{|c|l|} 
\hline
Symbol & Meaning \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & object size constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=\langle O:T \rangle$ & pattern with object set $O$, time sequence $T$\\
\hline
$\eta$ & replication factor in the TRPM framework\\
\hline
$C_t(o)$ & the cluster of object $o$ at time $t$ \\
\hline 
$S_t$ & the set of clusters at time $t$\\
\hline 
$\lambda_t$ & the partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
\hline
$Sr_i $ &  the star partition for object $i$ \\
\hline 
\end{tabular} 
\caption{Symbols and notions used}
\end{table}

>>>>

We take $T=(1,2,3,5,6)$ as an example, which can be decomposed into two segments $(1,2,3)$ and $(5,6)$. $T$ is not $3$-consecutive since the length of $(5,6)$ is $2$. Thus, it is safe to say either $T$ is $1$-consecutive or $2$-consecutive. On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring timestamps is $2$. It is worth noting that $T$ is not $1$-connected because the gap between $T[3]$ and $T[4]$ is $2$ (i.e., $5-3=2$).

Given a trajectory database discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textit{significance:} $|O| \geq M$; (3) \textit{duration:} $|T| \geq K$; (4) \textit{consecutiveness:} $T$ is $L$-consecutive; and (5) \textit{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$.  By customizing these parameters, our pattern can 
express other patterns proposed in the previous literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we achieve the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
\textbf{Pattern} & $M$ & $K$ & $L$ & $G$ & \textbf{Clustering} \\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & Disk-based\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & Disk-based \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & Density-based\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & Density-based \\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & Density-based\\ 
\hline 
\end{tabular} 
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value. $M$ represents the 
object \emph{size} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.}
\label{tbl:patterns}
\end{table}
\eat{ 
It is also observable that the number of patterns in GCMP could be exponential under some parameter settings (i.e., 
when expressing \emph{swarm}). In particular, given a parameter $M$, if a pattern $P$ is valid, then any subset of $P$ with 
size $M$ is also a valid pattern. This results in additional $\Sigma_{M\geq i \geq |P.O|} {|P.O| \choose i}$ patterns,
which is clearly overwhelming and redundant. For all these patterns, output $P$ is sufficient. Therefore, we define the \emph{Closed General Co-Movement Pattern} as follows:

@@

Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
We currently expose both disc-region based clustering and DBSCAN as options to the users. In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMPs from large-scale trajectory databases. Before we move on to the algorithmic part, we list the notations that are used in the following sections.

\begin{table}[h]\scriptsize
\centering
\begin{tabular}{|c|l|} 
\hline
\textbf{Symbol} & \textbf{Meaning} \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & significance constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=\langle O:T \rangle$ & pattern with object set $O$, time sequence $T$\\
\hline
$C_t(o)$ & cluster of object $o$ at time $t$ \\
\hline 
$S_t$ & set of clusters at time $t$\\
\hline 
$\lambda_t$ & partition with snapshots $S_t,..,S_{t+\eta-1}$ \\\hline
$\eta$ & replication factor in the TRPM framework\\
\hline
$Sr_i $ &  star partition for object $i$ \\
\hline 
$\Gamma$ & size of the largest star in star partition \\
\hline
\end{tabular} 
\caption{Symbols and notions used}
\end{table}

### 2016-06-29 sec4_baseline.tex
Several minor changes
Needs to proofread more

\begin{theorem}
\label{THM:RP_ETA}
$\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$ guarantees that no valid pattern is missing.
\end{theorem}
\begin{proof}
Given a valid pattern $P$, we can always find at least one valid subsequence that is also valid. Let $T'$ denote the valid subsequence with the minimum length. In the worst case, $T'=P.T$. We define $\range(T)=\max(T) - \min(T) +1$ and prove the theorem by showing that $\range(T') \leq \eta$.
Since $T'$ can be written as a sequence of L-consecutive segments interleaved by gaps: $l_1,g_1,\ldots,l_{n-1},g_{n-1},l_n$ ($n \geq 1$),
where $l_i$ is a segment and $g_i$ is a gap. Then, $\range(T')$
is calculated as $\Sigma_{i=1}^{i=n}|l_i| + \Sigma_{i=1}^{i=n-1} |g_i|$. Since $T'$
is valid, then $\Sigma_{i=1}^{i=n}|l_i| \geq K$. As $T'$ is minimum, if we remove the 
last $l_n$, the resulting sequence should not be valid. Let $K' = \Sigma_{i=1}^{i=n-1}|l_i|$, which
is the size of the first $(n-1)$ segments of $T'$. Then, $K' \leq K-1$.
Note that every $|l_i| \geq L$, thus $n \leq \lceil \frac{K'}{L} \rceil \leq \lceil \frac{K}{L} \rceil $. By
using the fact that every $|g_i| \leq G-1$, we achieve $\Sigma_{i=1}^{i=n-1} |g_i| \leq (n-1)(G-1)
\leq (\lceil \frac{K}{L} \rceil -1)(G-1)$. Next, we consider the difference between $K$ and $K'$, denoted by
$\Delta = K- K'$. To ensure $T'$'s validity, $l_n$ must equal to $\min(L, \Delta)$.
Then, $\Sigma_{i=1}^{i=n}|l_i| = K' + l_n = K - \Delta + \min(L, \Delta) \leq K - 1 + L$. We finish showing $\range(T') \leq \eta$.  Therefore, for any valid sequence $T$, it exists at least one valid subsequence with range no greater than $\eta$ and hence this pattern can be detected in a partition with $\eta$ snapshots.
\end{proof}

@@

The complete picture of temporal replication and parallel mining is summarized in Algorithm~\ref{algo:trm_overview}. We illustrate the workflow of the TRPM method using Figure~\ref{fig:trm} (c) and (d) with pattern
parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+2K - 2 = 5$. Therefore, 
in Figure~\ref{fig:trm}(c), every $5$ consecutive snapshots are combined 
into a partition in the map phase. In Figure~\ref{fig:trm}(d), a line sweep
method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set when sweeping snapshot $S_i$.
Initially, $C_1$ contains patterns with object sets in snapshot $S_1$.
As we sweep the snapshots, the patterns in $C_i$ grow. At snapshot $S_4$, the candidate
$\langle o_5,o_6 \rangle$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
and the next scanning timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
Next, at snapshot $S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed. This is
because its local consecutive segment $(4)$ has only $1$ element,
which violates the $L$-consecutive constraint.
Finally, $\langle o_3,o_4 \rangle$ is the valid pattern and is returned. Note that in this example, $\eta=5$ is the minimum setting that can guarantee correctness. If $\eta$ is set to $4$, the pattern $\langle o_3,o_4 \rangle$ would be missed.

>>>>

\begin{theorem}
\label{THM:RP_ETA}
$\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$ guarantees that no valid pattern is missing.
\end{theorem}
\begin{proof}
Given a valid pattern $P$, we can always find at least one valid subsequence of $P.T$ that is also valid. Let $T'$ denote the valid subsequence of $P.T$ with the minimum length. In the worst case, $T'=P.T$. We define $\range(T)=\max(T) - \min(T) +1$ and prove the theorem by showing that $\range(T') \leq \eta$.
Since $T'$ can be written as a sequence of L-consecutive segments interleaved by gaps: $l_1,g_1,\ldots,l_{n-1}$, $g_{n-1},l_n$ ($n \geq 1$),
where $l_i$ is a segment and $g_i$ is a gap. Then, $\range(T')$
is calculated as $\Sigma_{i=1}^{i=n}|l_i| + \Sigma_{i=1}^{i=n-1} |g_i|$. Since $T'$
is valid, then $\Sigma_{i=1}^{i=n}|l_i| \geq K$. As $T'$ is minimum, if we remove the 
last $l_n$, the resulting sequence should not be valid. Let $K' = \Sigma_{i=1}^{i=n-1}|l_i|$, which
is the size of the first $(n-1)$ segments of $T'$. Then, $K' \leq K-1$.
Note that every $|l_i| \geq L$, thus $n \leq \lceil \frac{K'}{L} \rceil \leq \lceil \frac{K}{L} \rceil $. By
using the fact that every $|g_i| \leq G-1$, we achieve $\Sigma_{i=1}^{i=n-1} |g_i| \leq (n-1)(G-1)
\leq (\lceil \frac{K}{L} \rceil -1)(G-1)$. Next, we consider the difference between $K$ and $K'$, denoted by
$\Delta = K- K'$. To ensure $T'$'s validity, $l_n$ must equal to $\min(L, \Delta)$.
Then, $\Sigma_{i=1}^{i=n}|l_i| = K' + l_n = K - \Delta + \min(L, \Delta) \leq K - 1 + L$. We finish showing $\range(T') \leq \eta$.  Therefore, for any valid sequence $T$, it exists at least one valid subsequence with range no greater than $\eta$ and hence this pattern can be detected in a partition with $\eta$ snapshots.
\end{proof}

@@

The complete picture of temporal replication and parallel mining is summarized in Algorithm~\ref{algo:trm_overview}. We illustrate the workflow of the TRPM method using Figure~\ref{fig:trm} (c) and (d) with pattern
parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+ K + L - 1 = 5$. Therefore, 
in Figure~\ref{fig:trm}(c), every $5$ consecutive snapshots are combined 
into a partition in the map phase. In Figure~\ref{fig:trm}(d), a line sweep
method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set when sweeping snapshot $S_i$.
Initially, $C_1$ contains patterns with object sets in snapshot $S_1$.
As we sweep the snapshots, the patterns in $C_i$ grow. At snapshot $S_4$, the candidate
$\langle o_5,o_6 \rangle$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
and the next scanning timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
Next, at snapshot $S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed. This is
because its local consecutive segment $(4)$ has only $1$ element,
which violates the $L$-consecutive constraint.
Finally, $\langle o_3,o_4 \rangle$ is the valid pattern and is returned. Note that in this example, $\eta=5$ is the minimum setting that can guarantee correctness. If $\eta$ is set to $4$, the pattern $\langle o_3,o_4 \rangle$ would be missed.

### 2016-06-29 sec6_experiment.tex
Several minor changes
Needs to proofread more

\subsubsection{Load Balance}
To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method. In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
Figure~\ref{exp:wl}(a) shows the breakdown of the costs in the map-reduce stages for SPARE and SPARE-RD. We observe that the map and shuffle time of SPARE and SPARE-RD are identical. The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost). We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.

>>>>

\subsubsection{Load balance}
To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method. In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
Figure~\ref{exp:wl}(a) shows the breakdown of the costs in the map-reduce stages for SPARE and SPARE-RD. We observe that the map and shuffle time of SPARE and SPARE-RD are identical. The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost). We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
